---
title: "Data Driven Business"
author: "Carlos Ram\'irez"
date: "December 18, 2017"
output:
  html_document: default
---


## Intro

The aim of this report is to find the main variables associated to business 
performance for the implementation of data driven decisions. 


## Results 

To simplify the analysis and avoid variable confusors we focused in the top 9
categories which accounts for the 80 percenatge of sales in the last year, further referred as the Pareto categories. This categories are comprised by Albanil, Plomero, Carpintero, Impermeablizador, Tablaroca y recubrimiento,
Pintor, Reparaci\'on de L\'inea Blanca y Electricista as shown in the next figure. 


```{r echo=FALSE,message=FALSE}

library(dplyr)
library(ggplot2)

## loading data from ifix model and timmings (chart Cumulative categoria )
url <- 'https://app.periscopedata.com/api/iguanafix/chart/csv/e5489dfe-e216-c950-6979-8b2e26f7e996/322144'
revenues <- read.csv(file=url)
revenues <- arrange(revenues,desc(facturacion))
revenues <- mutate(revenues, categoria=factor(categoria,levels=categoria))
revenues <- mutate(revenues,cumulative=cumsum(facturacion))
revenues <- mutate(revenues,facturacionPerc= 100.0*facturacion/sum(facturacion))
revenues <- mutate(revenues,cumulativePerc=100.0*cumulative/sum(facturacion))
revenues <- revenues[1:12,]

theme_set(theme_classic())
g <- ggplot(revenues,aes(x=categoria,y=cumulativePerc,group=1)) + geom_area(color='green',fill='green')
g <- g + geom_bar(data=revenues,aes(x=categoria,y=facturacionPerc,fill=categoria),stat='identity')
g <- g + theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
g <- g + labs(y='GMV Percentage',title='Pareto Categories')
g
```

```{r}
library(dplyr)
url <- 'https://app.periscopedata.com/api/iguanafix/chart/csv/4c63dbb5-90c0-a945-d767-09970e05f738'
revenues <- read.csv(file=url)
revenues$
plomero <- filter(revenues,categoria=='Plomero')
hyst(plomero$Facturacion)
```

