---
title: "Pending times"
author: "Carlos Ram?rez"
date: "December 5, 2017"
output:
  html_document: default
  word_document: default
---

# Abstract

Pending times are very important for customer experience and fidelity. Hence, in this EDA report we analyze
pending times for bussiness step processes in order to monitore and evaluate businness steps
performance. In this report we focuses in Pareto categories, that is, top categories that accounts for more than eighty percent of the total GMV in the year 2017.


# Results

## Pending times across ifix steps

The following figure shows the pending times for diverse ifix steps.

``` {r echo=FALSE, message=FALSE, warning=FALSE}

library(devtools)
library(plotFun)
library(ggplot2)
library(dplyr)
library(reshape2)

## 
timmings <- read.csv("https://app.periscopedata.com/api/iguanafix/chart/csv/00eb5d3c-6c3d-1433-8397-c5e5c4343828")

``` 


 The logarithm of the pending times are shown in the next figure, it can be seen that the process from visit to quote pdf attachment to ifix platform has the biggest mean pending time (267 hours ~ 11 days) of all the process steps in 2017. However, all steps have much variation 
(from 3 to 124, taking exponents). The time from payment to the initiation of the custom project has the lower mean values (142 hours ~ 6 days). 

```{r echo=FALSE, message=FALSE}

timmings.mex <- filter(timmings,currency=='MXN')

timmings.mx <- filter(timmings,currency=='MXN')
timmings.mx <- filter(timmings.mx,0 < visit2quote)
timmings.mx <- filter(timmings.mx,0 < ordvisit2ord)
timmings.mx <- filter(timmings.mx,0 < ord2project)
timmings.mx <- filter(timmings.mx,0 < paid2project)
timmings.mx <- filter(timmings.mx, category %in% c('Plomero',
                                                   'Albañil',
                                                   'Carpintero',
                                                   'Tablaroca y recubrimientos',
                                                   'Impermeabilizar',
                                                   'Pintor') )
timmings.mx <- select(timmings.mx, visit2quote:paid2project)
timmings.melt <- melt(timmings.mx)

theme_set(theme_classic())
g <- ggplot(timmings.melt, aes(x=variable,y=log(value+1))) 
g <- g + geom_boxplot(aes(fill=factor(variable)))
g <- g + labs(title='Timmins per ifix step',
              x='Ifix Step',
              y='Log(Pending time)',
              fill='ifix Step')
plot(g)

mex <- filter(timmings,currency=='MXN')


visit2quote.sum <- summary(mex$visit2quote)
ordvisit2ord.sum <- summary(mex$ordvisit2ord)
ord2project.sum <- summary(mex$ord2project)
paid2project.sum <- summary(mex$paid2project)
timmming.sum <- cbind(ordvisit2ord.sum,ord2project.sum,visit2quote.sum,paid2project.sum)
timmming.sum
```

## Pending times across categories

In the following figure pending times (logs) by categories are shown. It can be seen that Limpieza (cleanning)
has low pending times and also a lot of variation in time values. At the other hand Plomero (plumbing) has low pending time. These two categories distributions differs in a unpaired t-test with a p-value = 4.496e-08 statistical test. 

```{r echo=FALSE, message=FALSE}
timmings.mx <- filter(timmings,currency=='MXN')
timmings.mx <- filter(timmings, category %in% c('Albañil',
                                                'Plomero',
                                                'Carpintero',
                                                'Tablaroca y recubrimientos',
                                                'Pintor',
                                                'Impermeabilizar'))
timmings.mx <- filter(timmings.mx,0 < visit2quote)
timmings.mx <- select(timmings.mx, category:visit2quote)
timmings.melt <- melt(timmings.mx)

theme_set(theme_classic())
g <- ggplot(timmings.melt, aes(x=category,y=log(value+1))) 
g <- g + geom_boxplot(aes(fill=factor(category)))
g <- g + labs(title='Timmings per ifix step',
              x='Categories',
              y='Log(Pending time)',
              fill='Category')
g <- g + theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
plot(g)


```


``` {r echo=FALSE}
test <-  t.test(timmings.mx[timmings.mx$category=='Pintor','visit2quote'],
                timmings.mx[timmings.mx$category=='Plomero','visit2quote'])
test
```


``` {r echo=FALSE}
test <-  t.test(timmings.mx[timmings.mx$category=='Tablaroca y recubrimientos','visit2quote'],
                timmings.mx[timmings.mx$category=='Plomero','visit2quote'])
test
```

## Conclusions

From the analysis it can be seen that 'Pintor' and 'Plomero' categories differ in pending time distribution, having 'Plomero' category lower response time (p-value = 1.756e-09). At the other hand, 'Plomero' and 'Tablaroca y recubrimientos' does not differ according to the statistical test (p-value = 0.1559). 'Pintor' category seems to be susceptible to standardization to improve quote pending times. A perspective of this work is to evaluate whether the response time is associated to a succesful sale.
